{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-16 draft.tex
Revised the introduction.

\begin{comment}
Maybe the goal of this work is to public a journal paper about a
practical solution for a drone to follow a single target. For this, we need
\begin{itemize}
\item A vision-based, single target tracking algorithm.
\item Other components for making a drone follow a target.
\begin{itemize}
\item An architecture diagram
\item Descriptions of vehicle control, motion planning, behavior
  generation, estimation of relative geometry between a drone and a
  target, etc
\item Experimental results or example videos
\end{itemize}
\end{itemize}

For the BMVC-17 submission, we're going to just focus on the first
part. This is because we need to build a drone for the second part.
\end{comment}

@@

The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target. The recent examples of the tracking-by-detection algorithms
include Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods learn
the model of the target's appearance on the fly while discriminating
the target from the background.

@@

\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

\item Since our visual tracker mostly focuses on tracking objects from
  aerial moving platforms, we design a new robust target-to-camera
  distance estimation method. This way, a safe distance between the
  target and the camera-platform can be preserved.

>>>>

\begin{comment}
Maybe the goal of this work is to publish a journal paper about a
practical solution for a drone to follow a single target. For this, we
need some descriptions on
\begin{itemize}
\item A vision-based, single target tracking algorithm.
\item Other components for making a drone follow a target.
\begin{itemize}
\item An architecture diagram
\item Descriptions of vehicle control, motion planning, behavior
  generation, estimation of relative geometry between a drone and a
  target, etc
\item Experimental results or example videos
\end{itemize}
\end{itemize}

For the BMVC-17 submission, we're going to just focus on the first
part -- a vision-based, single target tracking algorithm. This is
because we need to build a drone for the second part.
\end{comment}

@@

The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target.

The recent examples of the tracking-by-detection algorithms include
Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods learn
the model of the target's appearance on the fly while discriminating
the target from the background.

@@

\item \textbf{Single-Target Tracking in High-Speed} To be practical,
  the execution time of an object tracking is important. We proposed a
  new object tracking algorithm that is a collection of kernelized
  correlation filters (KCF). Each of KCFs is designed to address two
  challenges of object tracking: scale and translation. We also
  incorporate a Bayes filter to prevent from being drift.

\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\begin{comment}
\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

\item Since our visual tracker mostly focuses on tracking objects from
  aerial moving platforms, we design a new robust target-to-camera
  distance estimation method. This way, a safe distance between the
  target and the camera-platform can be preserved.
\end{comment}
